Dike experiment

### 2023-01-25 manuscript.Rmd
Update manuscript.Rmd

We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates). The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)). The split plot was caused by testing all 24 treatments on both sides of the dike. We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs. 30 cm). Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed. The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:substrate)). The two seed mixture types were tested with two seeding densities (4 vs. 8 g^-2^). The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976]. Establishment rates of species (Appendix Table \@ref(fig:table-establishment)).

@@

Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our owen surveys in the surroundings on Danube dikes [@bauer2023]. We chose

@@

A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time. Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21). <!--# Refer to Table Sx -->

@@

All analyses were performed in R [Version 4.2.2; @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].

<mark>To identify the final model, we first reviewed the residual diagnostics of the candidate models and subsequently compared the remaining models using the Akaike information criterion adjusted for a small sample size (AICc) and chose the most parsimonious model. Finally, we calculated the marginal and conditional coefficients of determination (R²m, R²c) and the 95% confidence intervals of the response variables.</mark> <!--# Explain model selection -->

>>>>

We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition, halfway up the slopes of the dike and arranged in six blocks (= replicates). The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)). The split plot was caused by testing all 24 treatments on both sides of the dike. We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs. 30 cm). Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed. The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(tab:substrate)). The two seed mixture types were tested with two seeding densities (4 vs. 8 g^-2^). The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964] and Londo scale was used [@londo1976]. Establishment rates of species (Appendix Table \@ref(fig:table-establishment)).

@@

Reference vegetation surveys were extracted from sPlotOpen [@Sabatini.2021] and our own surveys in the surroundings on Danube dikes [@bauer2023]. We selected six calcareous grassland plots [EUNIS code R1A, @Chytry.2020] within SE Germany from sPlotOpen and 98 plots of our own survey which included furthermore lowland hay meadows (R22) and as a negative reference ruderal, dry and anthropogenic vegetation (V38).

@@

A non-metric multidimensional scaling ordination (NMDS) with Jaccard dissimilarity was used to visualize variation in species composition in space and time. Rare species with an accumulated cover over all plots of less than 0.5% were excluded (2D-stress: 0.21).

@@

All analyses were performed in R [Version 4.2.2, @base] with the functions 'brm' from the package 'brms' [@brms] for model calculation, several functions from 'brms' and 'bayesplot' [@bayesplot] for model evaluation and 'metaMDS' from 'vegan' for the ordination [@vegan].
